### 2014-11-02 thesis/thanks/thanks.tex
Minor fix to acknowledgements

And, last but not least -- to my parents Caixiu and Ning, and
my sister Lily -- thank you for tirelessly supporting me throughout this year,
especially towards the end. This would not have been possible without all of
you.

>>>>

And, last but not least -- to my parents Caixiu and Ning, and
my sister Lily -- thank you for tirelessly supporting me throughout this year,
especially towards the deadline. This would not have been possible without all
of you.
